\section*{NeurIPS Paper Checklist}

\begin{enumerate}

\item {\bf Claims}
    \item[] Question: Do the main claims made in the abstract and introduction accurately reflect the paper's contributions and scope?
    \item[] Answer: \answerYes{}
    \item[] Justification: The abstract and introduction state empirical claims (same-dataset re-ID reduction, FM-utility preservation, cross-dataset APG) supported by Tables~\ref{tab:privacy_tueg}, \ref{tab:fm_utility}, and \ref{tab:crossdataset}. The framing is explicitly empirical, not formal.

\item {\bf Limitations}
    \item[] Question: Does the paper discuss the limitations of the work performed by the authors?
    \item[] Answer: \answerYes{}
    \item[] Justification: Section~\ref{sec:discussion} discusses training scale, FM ensemble size, cross-dataset FM-utility scope, and the VQ-tokenizer downgrade caveat.

\item {\bf Theory assumptions and proofs}
    \item[] Answer: \answerNA{}
    \item[] Justification: NeuroVeil-U is an empirical systems contribution; no formal privacy theorems are claimed.

\item {\bf Experimental result reproducibility}
    \item[] Answer: \answerYes{}
    \item[] Justification: Section~\ref{sec:setup} and Appendix~\ref{app:training} specify all hyperparameters and architecture details. Appendix~\ref{app:fm_ckpts} lists exact teacher checkpoint paths.

\item {\bf Open access to data and code}
    \item[] Answer: \answerYes{}
    \item[] Justification: Code and checkpoints will be released upon acceptance; TUEG/TUAB/TUSL/HMC are public.

\item {\bf Experimental setting/details}
    \item[] Answer: \answerYes{}
    \item[] Justification: Sections~\ref{sec:curriculum}, \ref{sec:setup}, and Appendix~\ref{app:training}, \ref{app:loss_weights}.

\item {\bf Experiment statistical significance}
    \item[] Answer: \answerNA{}
    \item[] Justification: Single training run per configuration, standard for privacy filters; multi-seed is future work.

\item {\bf Experiments compute resources}
    \item[] Answer: \answerYes{}
    \item[] Justification: Section~\ref{sec:setup} specifies single A40, training time budgets per phase.

\item {\bf Code of ethics}
    \item[] Answer: \answerYes{}

\item {\bf Broader impacts}
    \item[] Answer: \answerYes{}
    \item[] Justification: Section~\ref{sec:discussion} covers both benefits (enabling clinical-EEG FM pretraining data sharing) and risks (not a formal anonymizer).

\item {\bf Safeguards}
    \item[] Answer: \answerYes{}
    \item[] Justification: Section~\ref{sec:discussion} positions NeuroVeil-U as a layer in an expert-determination workflow.

\item {\bf Licenses for existing assets}
    \item[] Answer: \answerYes{}
    \item[] Justification: Each FM checkpoint is loaded from its official public release with its licence honored.

\item {\bf New assets}
    \item[] Answer: \answerYes{}
    \item[] Justification: Code and documentation will be released with the paper.

\item {\bf Crowdsourcing and research with human subjects}
    \item[] Answer: \answerNA{}

\item {\bf IRB approvals}
    \item[] Answer: \answerNA{}
    \item[] Justification: No new human-subject data collection; all datasets are standard research corpora with their own IRB provenance.

\item {\bf Declaration of LLM usage}
    \item[] Answer: \answerNA{}
    \item[] Justification: LLMs are not a component of NeuroVeil-U's method.

\end{enumerate}
