%=============================================================
\section{Related work}
\label{sec:related}
%=============================================================

\paragraph{EEG foundation models.} Large-scale self-supervised pretraining on EEG has produced a fast-moving family of foundation models that split cleanly by pretraining objective. Continuous masked autoencoders include EEGPT~\citep{eegpt}, CBraMod~\citep{cbramod}, REVE~\citep{reve}, EEG-X, and LUNA~\citep{luna}. Vector-quantized (VQ) tokenization appears in LaBraM~\citep{labram} with an 8192-code neural tokenizer, CodeBrain~\citep{codebrain} with dual temporal and frequency codebooks, TFM-Tokenizer~\citep{tfm_tokenizer}, NeuroLM~\citep{neurolm}, and BrainRVQ. Contrastive / cross-modality transformers are represented by BIOT~\citep{biot}. Recent benchmarks~\citep{eeg_fm_bench} show that FMs from different paradigms rank inconsistently across downstream tasks, but none of these benchmarks measures identity leakage under post-filter inputs, which motivates our FM-representation attacker protocol.

\paragraph{EEG privacy filters.} Bounded-perturbation filters for EEG identity suppression include User-wise Perturbations~\citep{unlearnable_eeg_meng}, ID-RemovalNet~\citep{wang2025idremovalnet}, A3E~\citep{a3e_eeg}, and Bridging Privacy \& Utility~\citep{bridging_privacy_utility}. All of these papers (i) use a CNN backbone of fixed channel count, (ii) train and evaluate attackers within a single dataset, and (iii) define utility via either raw-signal MSE or a single task-specific classifier. Our 13-head adversary set and cross-dataset evaluation protocol are compatible with each of these methods and we use them as baselines.

\paragraph{Domain generalization and adversarial censoring.} The dataset-adversarial / gradient-reversal mechanism we use as the site-DANN head follows \citet{ganin2015_dann}. For EEG utility, domain-adversarial learning across sites is well-established~\citep{exploiting_multi_eeg_domains}, but to our knowledge no prior privacy filter combines it with an identity-adversarial objective. Related channel-agnostic encoders for EEG include REVE~\citep{reve} and LUNA~\citep{luna}, which we adapt for generator use rather than encoder use.

\paragraph{Distillation as a privacy-friendly interface.} Function-tangent knowledge distillation~\citep{flex_kd} and cross-architecture representation matching have been used for transfer across model families, but not yet as a utility surrogate for privacy filters. Our Ensemble Functional Surrogate $\Estar$ can be viewed as a multi-teacher Flex-KD student that is additionally shaped to the VQ-soft-KL geometry of tokenized teachers. Concurrent work in speech~\citep{stabletoken} documents that semantic VQ tokenizers are surprisingly fragile under small perturbations---the same structural property that a MSE-only privacy filter fails to probe, and that motivates our VQ-aware utility head.
