%=============================================================
\section{Discussion and limitations}
\label{sec:discussion}
%=============================================================

\paragraph{What the Ensemble Functional Surrogate buys us.} A naive implementation of multi-FM utility preservation would forward five teachers per training step, costing roughly $5\times$ extra memory and compute. By distilling those five outputs into a single student $\Estar$ whose architecture matches the generator's encoder, the Phase-2 loss $\mathcal{L}_\star^{\text{geom}}$ reduces to one additional forward through a trunk of size comparable to the generator itself. This makes the ambitious ``FM-agnostic'' thesis practically trainable rather than an asymptotic target.

\paragraph{Nature of the empirical privacy claim.} We report \emph{empirical} identity suppression under retrained DeepCNN, FM-representation probe, and site-classifier attackers. The architectural perturbation bound $\|\Xt\!-\!X\|_\infty\!\le\!\delta$ constrains distortion but does not yield a formal $(\varepsilon,\delta)$-differential-privacy guarantee. NeuroVeil-U should be positioned as a \emph{controlled-release privacy layer}: one technical component of a broader expert-determination workflow, not a standalone anonymizer.

\paragraph{The VQ-tokenizer head caveat.} Our LaBraM and CodeBrain heads are auto-downgraded to continuous regression on the teacher's embedding whenever the \texttt{vqnsp.pth} tokenizer cannot be loaded (e.g.\ because an importable factory function is missing in the public release). This happens in our environment for LaBraM's VQ tokenizer; the embedding-level continuous head still preserves downstream transfer quality but does not directly supervise code-flip rate. A follow-up version with a successfully loaded frozen VQ tokenizer is a natural extension.

\paragraph{Limitations.}
\textbf{(1)~Training scale.} Our reported numbers are from 500-TUEG-subject training for compute reasons. At full 2000-subject V4 training scale we expect similar qualitative trends but stronger absolute numbers. \textbf{(2)~FM ensemble size.} We use 5 teachers; NeuroLM, TFM-Tokenizer, EEG-X, and BrainRVQ are natural additions once their official checkpoints are stably available. \textbf{(3)~Cross-dataset FM utility.} We report FM linear-probe utility on TUAB only; HMC/SEED linear-probe utility is a follow-up. \textbf{(4)~Montage subsampling.} The generator sees $C_{\text{sub}}\!\in\![8,19]$ during training; HMC's 4-channel bipolar inputs at evaluation push beyond this range, and the current zero-shot transfer to HMC is the weakest point of the pipeline.

\paragraph{Broader impact.} By making EEG privacy filters paradigm-agnostic---preserving the latent geometry of tokenized, continuous-MAE, and contrastive foundation models simultaneously---NeuroVeil-U reduces the barrier to contributing clinical EEG to shared foundation-model pretraining pools. However, empirical identity suppression is not formal anonymization: filtered data should still be subject to institutional access controls and data use agreements, and should not be treated as safe for unrestricted release.
